---
title: "Presentation"
date: "`r Sys.Date()`"
author: "RE07N2"
format: revealjs


  
---

## import data
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(MASS)
library(janitor)
library(knitr)
library(ggpubr)
library(ggfortify)
library(sjPlot)
library(caret)
library(qtlcharts)

theme_set(theme_bw())
data = read.delim("housing-prices-ge19.txt", header = T, sep = "\t")
```

```{r}
glimpse(data)
```

## clean data
```{r}
data = remove_empty(data)
data = data %>%
  janitor::clean_names()
data
```


```{r}
summary(data$price)
```

## Initial data analysis
```{r}
delete_data = dplyr::select(data, -c(fuel_type,heat_type,sewer_type))
clean_data = remove_empty(delete_data)
clean_data = delete_data %>% 
  janitor::clean_names()

qtlcharts::iplotCorr(clean_data)

```

```{r}
p = ggplot(data = data, aes(x ="", y =price))
p + geom_boxplot(notch = TRUE, outlier.colour = "lightblue", fill = "gold", outlier.shape =5, outlier.size = 2) +
  labs(y = "House Price in New York",
       title = "Box plot for House Price in New York")

```



## Model 1 (linear-linear(full))
```{r}
lm1 = lm(price ~ ., data = data)
summary(lm1)
```
```{r}
autoplot(lm1, which = 1:2) + theme_bw()
```


## Model 2 (linear-linear model after variable selection)
```{r}
M0 = lm(price ~ 1, data = data)
M1 = lm(price ~ ., data = data)

# backward selection
backward = step(M1, direction = "backward", trace = FALSE)
summary(backward)

# forward selection
forward = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
summary(forward)
```

## Model 3 (linear-log)
```{r}
data = data %>%
mutate(loland_value = log(land_value))
lm3 = lm(price ~ lot_size + waterfront + loland_value + living_area + bathrooms + new_construct, data)
summary(lm3)
```


## Model 4 (log-linear)
```{r}
data = data %>%
mutate(loPrice = log(price))
lm4 = lm(loPrice ~ lot_size + land_value + waterfront + new_construct + living_area + bathrooms, data)
summary(lm4)
```


## Model 5 (log-log)
```{r}
data = data %>%
mutate(lorland = log(land_value)) # log(land.value)
data = data %>%
mutate(lorrice = log(price)) #log(price)
lm5 = lm(lorrice ~ lot_size + waterfront + lorland + new_construct + living_area + bathrooms, data)
summary(lm5)
```


## Appropriate model selection
```{r}
sjPlot::tab_model(lm1, forward, lm3, lm4, lm5, digits = 3, show.ci = FALSE)
```
```{r}
# linear-linear
cv_1 = train(
  price ~ lot_size + land_value + waterfront + new_construct + living_area + bathrooms, data, method ="lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_1
```

```{r}
# linear-log
cv_2 = train(
  price ~ lot_size + waterfront + loland_value + living_area + bathrooms + new_construct, data, method = "lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_2
```

```{r}
# log-linear
cv_3 = train(
  loPrice ~ lot_size + land_value + waterfront + new_construct + living_area + bathrooms, data, method = "lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_3
```

```{r}
# log-log
cv_4 = train(
  lorrice ~ lot_size + waterfront + lorland + new_construct + living_area + bathrooms, data, method = "lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_4
```

## Assumption check
```{r}
autoplot(lm5, which = 1:2) + theme_bw()
```

Linearity: 
There are some outliers occur in the plot. The residuals roughly form a "horizontal band" around the 0 line. This suggests that the variances of the error terms are equal. The equally spread residuals around a horizontal line without distinct patterns are a good indication of having the linear relationships.

Independence:
Based on the residuals versus fitted values plot, it shows that the relation can be consider as an independence observation. 

Homoskedasticity:
The residuals versus fitted values plot shows that the data is homoskedasticity, since the residual are spread along the range of predictors, and there was not a funnel shape in the plot. 

Normality:
The Normal Q-Q plot shows data sampled from a uniform distribution, which has "“lighter”" tails than a normal distribution and this is reflected in the points deviating from the line at the extremes of the QQ plot. The normality assumption is satisfied because the points in the QQ plot follow the line closely and therefore the residuals can reasonably be assumed to follow a normal distribution.

## Interpret the estimated coefficients
log(price) = 10.10335 + 0.03328 lot_size + 0.53084 waterfront + 0.12108 log(land_value) - 0.08690 new_construct + 0.00032 living_area + 0.14073 bathrooms

## Conclusion
