---
title: "House price in New York"
author: "RE07N2\n
        Ran Wang, Xu Huang, Chen-Yu Wang, Wancheng Liu, Jiyuan Liu"
date: "2022-10-23"
output:
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false # disable slide transitions by scrolling
---
## Table of content

1.Introduction

2.Data description

3.Modeling objectives

4.Model selections

5.Assumption check 

6.Conclusion


---

## Introduction


- Data resource: Full Saratoga Housing data 



- The aim of the report



- Target Group: Property development



---

## Data description

- Data resource: Full Saratoga Housing data 
- Important variables
```{r echo = FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(MASS)
library(janitor)
library(knitr)
library(ggpubr)
library(ggfortify)
library(sjPlot)
library(caret)
library(qtlcharts)

theme_set(theme_bw())

```

```{r echo = FALSE}
data = read.delim("housing-prices-ge19.txt", header = T, sep = "\t")
glimpse(data)
```



```{r echo = FALSE}
## clean data
data = remove_empty(data)
data = data %>%
  janitor::clean_names()

```

```{r echo = FALSE}
summary(data$price)
```



---

## Modeling objectives

- 5 models

1. linear-linear full model 
2. linear-linear null model
3. linear-log model
4. log-linear model
5. log-log model

- The goal of model


```{r echo = FALSE, message = FALSE}
## Model 1 (linear-linear(full))
lm1 = lm(price ~ ., data = data)
#summary(lm1)
```


```{r echo = FALSE, , message = FALSE}
#autoplot(lm1, which = 1:2) + theme_bw()
```




```{r echo = FALSE, message = FALSE}
## Model 2 (linear-linear model after variable selection)
M0 = lm(price ~ 1, data = data)
M1 = lm(price ~ ., data = data)

# backward selection
backward = step(M1, direction = "backward", trace = FALSE)
#summary(backward)

# forward selection
forward = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
#summary(forward)
```




```{r echo = FALSE, message = FALSE}
## Model 3 (linear-log)
data = data %>%
mutate(loland_value = log(land_value))
lm3 = lm(price ~ lot_size + waterfront + loland_value + living_area + bathrooms + new_construct, data)
#summary(lm3)
```




```{r echo = FALSE, message = FALSE}
## Model 4 (log-linear)
data = data %>%
mutate(loPrice = log(price))
lm4 = lm(loPrice ~ lot_size + land_value + waterfront + new_construct + living_area + bathrooms, data)
#summary(lm4)
```




```{r echo = FALSE, message = FALSE}
## Model 5 (log-log)
data = data %>%
mutate(lorland = log(land_value)) # log(land.value)
data = data %>%
mutate(lorrice = log(price)) #log(price)
lm5 = lm(lorrice ~ lot_size + waterfront + lorland + new_construct + living_area + bathrooms, data)
#summary(lm5)
```


---

## Appropriate model selection
```{r echo = FALSE}
sjPlot::tab_model(lm1, forward, lm3, lm4, lm5, digits = 3, show.ci = FALSE)
```

---

## log-linear model
```{r echo = FALSE}
# log-linear
cv_3 = train(
  loPrice ~ lot_size + land_value + waterfront + new_construct + living_area + bathrooms, data, method = "lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_3
```
---
## log-log model
```{r echo = FALSE}
# log-log
cv_4 = train(
  lorrice ~ lot_size + waterfront + lorland + new_construct + living_area + bathrooms, data, method = "lm",
  trControl = trainControl(method = "cv", number = 10,verboseIter = FALSE)
)
cv_4
```

---

## Assumption check
```{r echo = FALSE}
autoplot(lm5, which = 1:2) + theme_bw()
```

---

## Interpret the estimated coefficients
log(price) = 10.10335 + 0.03328 lot_size + 0.53084 waterfront + 0.12108 log(land_value) - 0.08690 new_construct + 0.00032 living_area + 0.14073 bathrooms

---

## Conclusion


- model: log - log


- Beneficiaries: property developers


- Limitations of the data

---
## Thank You!